Democratizing Secure Two-Party Computation

### 2017-10-12 OaklandSubmission/eval.tex
minor

The next class of classifiers that we discuss are deep neural nets or DNNs. 
A DNN has multiple layers such that each layer computes a matrix multiplication followed by an {\it activation} function $f$. The most common activation functions are square $f(x)=x^2$ and rectifier linear unit (ReLU) $f(x)=\mathsf{max}(x,0)$. 
If $A$ is a matrix then the output of $f(A)$ is also a matrix that is obtained by applying $f$ to each entry of $A$ pointwise.
Given an input vector $x$, the predicted label of a DNN is
\[
 \mathsf{argmax}\ W_N\cdot f_{N-1}(\ldots f_1(W_1\cdot x)\ldots)
\]
Here, $f_i$'s are the \divya{public} activation functions and the model consists of matrices $W_i$. The input vector is $x \in \R^d$.
The operator $\cdot$ denotes a matrix multiplication.
Neural nets usually have one or more fully connected layers.
These layers multiply a matrix with a vector.
Some neural nets have convolution layers and such DNNs are also called convolutional neural nets or CNNs.
For the purpose of this paper, a convolution can be considered as a (heavy) matrix-matrix multiplication. The size of matrices manipulated by a convolution layer grows linearly with {\it window size} (typically 9 or 25), the number of {\it output channels} (typically 16, 32, or 64), and the size of the matrix input to this layer. 
Therefore, fully connected layers are lighter computation-wise compared
to convolution layers. In general, DNNs are computationaly heavy but provide
much better accuracies on computer vision tasks than the classifiers discussed above.

@@

The results for linear classification are in Table~\ref{tab:lc}. The input and model are both vectors of length $d$. The time in columns ``Prev. time'' and communication ``Prev.Comm'' is the time and total network communication reported in~\cite{shafindss}. They remark that these times are obtained by simulating a network with 40ms round trip time, which is the same as our WAN setting. The total execution time of \tool generated code in the LAN and the WAN setting is reported next followed by the total communication.
The execution time is dominated by multiplications and boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the benchmarks as they reflect the number of and gates required for a single 32-bit integer comparison with zero. The number of multiplication gates (\#Mul) is the same as the model size $d$. The last column shows the lines of code of \tool program, which is also independent of the model size.

@@

 \caption{Linear classification results}
 \label{tab:lc} 
\end{table*}

@@

 \caption{Na\"{i}ve Bayes results}
 \label{tab:nb} 
\end{table*}

@@

 \caption{Decision tree benchmarks}
 \label{tab:dt} 
\end{table*}

@@

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
We evaluate \tool on the DNNs described in \minion~\cite{minionn} and the results are reported in Table~\ref{tab:nn}\footnote{\minion does not report the network round-trip time~\cite{minionn}.}.
Our goal here is to demonstrate that \tool
can provide performance competitive to specialized protocols for DNNs described in~\cite{secureml,cryptonets,minionn}. 
The first benchmark  is the DNN described in SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations (additions and multiplications)
except for the {\it argmax} at the end.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets} in \tool.
This DNN also uses square as the activation function and has one convolution (with 5 output channels) and one fully connected layer.
Finally, we compare against \minion on a CNN
with two convolutions (with 16 output channels each) and two fully connected layers.
In contrast to the previous two DNNs, this DNN uses ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using arithmetic gates but ReLU requires boolean-and gates.  For a complete description of these benchmarks,  the reader is referred to the original references.

For the benchmarks in Table~\ref{tab:nn}, \minion
outperforms SecureML and Cryptonets and columns 2 and 3 show the time taken by \minion.
We observe that our performance is competitive with \minion in the LAN and the WAN settings and the lines of code required are still small.
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient preprocessing phase and has SIMD
(single instruction multiple data) capabilities that allow \minion to perform
matrix operations efficiently. Our language and compiler are generic and we have none of these.
Although we could have used the SIMD capabilities of ABY to improve our performance---our preliminary evaluation suggests that SIMD could lead to a 2X performance improvement---we decided against it to avoid being closely tied to ABY and keeping \tool general, i.e., oblivious to the 2PC backend.
However, \minion also reports performance results on a bigger DNN with 7 convolution layers.
This benchmark requires pipelining and we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c}
Name  & Prev. time (s) & Prev. Comm (Mb) & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 7    & 2k    & 108k & 316k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 154\\
\hline
\end{tabular}

 \caption{DNN benchmarks}
 \label{tab:nn} 
\end{table*}

\subsection{Practical models}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of digits 0 to 9.
The first model that the tutorial describes is softmax regression
that provides an accuracy of 92\%. The classifier here evaluates
\[
 \mathsf{argmax}_{i} w_i^Tx+b_i
\]
Here, $i\in[0,9]\cap\mathbb{Z}$, $x$ is a 784 length vector obtained from the input image,
each $w_i$ is a 784 length vector, and each $b_i$ is a scalar. 
We implement this classifer in \tool and the results are shown in the first row of Table~\ref{tab:tf}.
Since, we are not familiar with any other tools that have used this model as a benchmark,
we only report execution time of \tool generated code.
The column ``Model size'' is the number of 32 bit integers in the trained model.

@@

Before discussing pipelining, we show \bonsai results on three standard datasets: character recognition (Chars4k~\cite{campos}, accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy 94.4\%), and object categorization (WARD~\cite{yang}, accuracy 95.7\%). 
The \bonsai models are already over integers and no port from floating-point is required.
We implement the trained classifiers in \tool for all benchmarks in~\cite{bonsai}
and show the represenative results in Table~\ref{tab:bonsai}.
Out of all benchmarks in~\cite{bonsai}, the dataset WARD requires the largest model.
The column ``depth'' in Table~\ref{tab:bonsai} shows the depth of the tree used by \bonsai. The size of \tool
program grows with the depth of the tree as the straightforward \tool implementation requires a
loop over the nodes of the tree and this loop needs to be unrolled.

>>>>

The next class of classifiers that we discuss are deep neural nets or DNNs. 
A DNN has multiple layers such that each layer computes a matrix multiplication followed by an {\it activation} function $f$. The most common activation functions are square $f(x)=x^2$ and rectifier linear unit (ReLU) $f(x)=\mathsf{max}(x,0)$. 
If $A$ is a matrix then the output of $f(A)$ is also a matrix that is obtained by applying $f$ to each entry of $A$ pointwise.
Given an input vector $x$, the predicted label of a DNN is
\[
 \mathsf{argmax}\ W_N\cdot f_{N-1}(\ldots f_1(W_1\cdot x)\ldots)
\]
Here, $f_i$'s are the \divya{public} activation functions and the model consists of matrices $W_i$. The input vector is $x \in \R^d$.
The operator $\cdot$ denotes a matrix multiplication.
Neural nets usually have one or more fully connected layers.
These layers multiply a matrix with a vector.
Some neural nets have convolution layers and such DNNs are also called convolutional neural nets or CNNs.
For the purpose of this paper, a convolution can be considered as a (heavy) matrix-matrix multiplication. The size of matrices manipulated by a convolution layer grows linearly with {\it window size} (typically 9 or 25), the number of {\it output channels} (typically 16, 32, or 64), and the size of the matrix input to this layer. 
Therefore, fully connected layers are lighter computation-wise compared
to convolution layers. However, the model size of fully connected layers is larger than those of convolution layers.
In general, DNNs are computationaly heavy but provide
much better accuracies on computer vision tasks than the classifiers discussed above.

@@

The results for linear classification are in Table~\ref{tab:lc}. The input and model are both vectors of length $d$. The time in columns ``Prev. time'' and communication ``Prev.Comm'' is the time and total network communication reported in~\cite{shafindss}. They remark that these times are obtained by simulating a network with 40ms round trip time, which is the same as our WAN setting. The total execution time of \tool generated code in the LAN and the WAN setting is reported next followed by the total communication.
We observe that \tool generated code has performance competitive to~\cite{shafindss}.
The execution time is dominated by multiplications and boolean-ands.
The number of boolean-and gates (\#And) remains constant for both the benchmarks as they reflect the number of and gates required for a single 32-bit integer comparison with zero. The number of multiplication gates (\#Mul) is the same as the model size $d$. The last column shows the lines of code of \tool program, which is also independent of the model size.

@@

 \caption{Linear classification results. We compare our results (columns 5, 6, 7) with~\cite{shafindss} (columns 3 and 4)}
 \label{tab:lc} 
\end{table*}

@@

 \caption{Na\"{i}ve Bayes results. We compare our results (columns 6 , 7, 8) with~\cite{shafindss} (columns 4 and 5)}
 \label{tab:nb} 
\end{table*}

@@

 \caption{Decision tree benchmarks. We compare our results (columns 5 , 6, 7) with~\cite{wu} (columns 3 and 4)}
 \label{tab:dt} 
\end{table*}

@@

%dataset | time | comm | timeL | timeW | comm
\subsection{Deep neural nets}
We evaluate \tool on the DNNs described in \minion~\cite{minionn} and the results are reported in Table~\ref{tab:nn}\footnote{\minion does not report the network round-trip time~\cite{minionn}.}.
Our goal here is to demonstrate that \tool
can provide performance competitive to specialized protocols for DNNs described in~\cite{secureml,cryptonets,minionn}. 
The first benchmark  is the DNN described in SecureML~\cite{secureml}.
It has three fully connected layers with square as the activation function.
This DNN is light-weight as it requires only arithmetic computations (additions and multiplications)
except for the {\it argmax} at the end.
Next, we implement the DNN described in Cryptonets~\cite{cryptonets} in \tool.
This DNN also uses square as the activation function and has one convolution (with 5 output channels) and one fully connected layer.
Finally, we compare against \minion on a CNN
with two convolutions (with 16 output channels each) and two fully connected layers.
In contrast to the previous two DNNs, this DNN uses ReLU for activation and
has significantly higher number of boolean-and gates.
Recall, that square activation can be implemented entirely using arithmetic gates but ReLU requires boolean-and gates.  For a complete description of these benchmarks and their accuracies,  the reader is referred to the original references.

For the benchmarks in Table~\ref{tab:nn}, \minion
outperforms SecureML and Cryptonets and columns 2 and 3 show the time taken by \minion. 
The column ``Model size'' is the number of 32 bit integers in the trained model.
We observe that our performance is competitive with \minion in the LAN and the WAN settings and the lines of code required are still small.
We note that \minion and \tool implementations are both based on ABY.
These results are surprising as \minion has a much more efficient preprocessing phase and has SIMD
(single instruction multiple data) capabilities that allow \minion to perform
matrix operations efficiently. Our language and compiler are generic and we have none of these.
Although we could have used the SIMD capabilities of ABY to improve our performance---our preliminary evaluation suggests that SIMD could lead to a 2X performance improvement---we decided against it to avoid being closely tied to ABY and keeping \tool general, i.e., oblivious to the 2PC backend.
However, \minion also reports performance results on a bigger DNN with 7 convolution layers.
This benchmark requires pipelining and we discuss it in Section~\ref{sec:pipeeval}.
%net | minionT | minionC | timeL | timeW | comm | gates | and | mul | length

\begin{table*}
\begin{tabular}{c|c|c|c |c|c|c|c|c|c|c}
Name  & Prev. time (s) & Prev. Comm (Mb) & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates & Model Size & LOC\\
\hline
SecureML   &  1.1 & 15.8 & 0.7 & 1.7  & 76   &  2k   & 119k & 366k   & 119k & 78\\
\hline
Cryptonets &  1.3 & 47.6 & 0.6 & 1.6  & 7    & 2k    & 108k & 316k & 86k & 88\\
\hline
CNN        &  9.4 & 657.5& 5.1 & 11.6 & 501  & 1640k & 667k & 9480k & 35k & 154\\
\hline
\end{tabular}

 \caption{DNN benchmarks. We compare our results (columns 4 , 5, 6) with~\cite{minionn} (columns 2 and 3)}
 \label{tab:nn} 
\end{table*}

\subsection{Practical models}
Tensorflow~\cite{tensorflow} is a standard machine learning toolkit.
Its introductory tutorial describes two prediction models for handwritten digit recognition
using the MNIST dataset~\cite{mnist}.
Each image in this dataset is a greyscale $28\times 28$ image of digits 0 to 9.
The first model that the tutorial describes is softmax regression
that provides an accuracy of 92\%. The classifier here evaluates
\[
 \mathsf{argmax}_{i} w_i^Tx+b_i
\]
Here, $i\in [10]$, $x$ is a 784 length vector obtained from the input image,
each $w_i$ is a 784 length vector, and each $b_i$ is a scalar. 
We implement this classifer in \tool and the results are shown in the first row of Table~\ref{tab:tf}.
Since, we are not familiar with any other tools that have used this model as a benchmark,
we only report execution time of \tool generated code.

@@

Before discussing pipelining, we show \bonsai results on three standard datasets: character recognition (Chars4k~\cite{campos}, accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy 94.4\%), and object categorization (WARD~\cite{yang}, accuracy 95.7\%). 
The \bonsai models are already over integers and no port from floating-point is required.
We implement the trained classifiers in \tool for all benchmarks in~\cite{bonsai}
and show the represenative results in Table~\ref{tab:bonsai}.
Out of all benchmarks in~\cite{bonsai}, the dataset WARD requires the largest model.
The column ``depth'' in Table~\ref{tab:bonsai} shows the depth of the tree used by \bonsai. The size of \tool
program grows with the depth of the tree as the straightforward \tool implementation requires a 
loop for each layer of the tree.

### 2017-10-12 OaklandSubmission/ex.tex
minor

The \tool compiler is fully automatic and compiles the code described in Figure~\ref{fig:ex-sml} to the C++ code that makes calls to the ABY library  in
Figure~\ref{fig:ex-aby}. An alternative to using \tool is to directly write this C++ code.
However, this code is much more complex than the implementation written in \tool.
Unlike \tool implementations, the ``secret" variables containing private data ({\tt w,x,b,acc}) need to be handled differently compared to public variables such as loop counters ({\tt i}). In particular, the former are manipulated by the ABY library and the latter are manipulated like standard  C++ variables.
Additionally, the C++ code branches on  the special variable
{\tt role}  to decide whether the enclosing code is executed by the {\tt SERVER} Bob or by
the {\tt CLIENT} Alice. In Figure~\ref{fig:ex-sml}, the developer does not need to
manipulate {\tt role} explicitly. In addition to simplifying the implementation, \tool prevents developers from writing buggy code such as\\
\verb+if(role == SERVER) {...manipulate x...}+

@@

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates. 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends.

>>>>

The \tool compiler is fully automatic and compiles the code described in Figure~\ref{fig:ex-sml} to the C++ code that makes calls to the ABY library  in
Figure~\ref{fig:ex-aby}. An alternative to using \tool is to directly write this C++ code.
However, this code is much more complex than the implementation written in \tool.
Therefore, it is difficult for Alice and bob to verify its correctness and security.
Unlike \tool implementations, the ``secret" variables containing private data ({\tt w,x,b,acc}) need to be handled differently compared to ``public" variables such as loop counters ({\tt i}). In particular, the former are manipulated by the ABY library and the latter are manipulated like standard  C++ variables.
Additionally, the C++ code branches on  the special variable
{\tt role}  to decide whether the enclosing code is executed by the {\tt SERVER} Bob or by
the {\tt CLIENT} Alice. In Figure~\ref{fig:ex-sml}, the developer does not need to
manipulate {\tt role} explicitly. In addition to simplifying the implementation, \tool prevents developers from writing buggy code such as\\
\verb+if(role == SERVER) {...manipulate x...}+

@@

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates (the cost of  conversion overweighs the gains of performing an arithmetic addition instead of a boolean addition). 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends. In particular,
ABY implements two party computation (2PC), i.e., SMC between two parties
and this paper focuses on this setting.
